
\documentclass[11pt,a4paper]{altacv}

\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{graphicx}
\usepackage{hyperref}

\definecolor{arsenic}{rgb}{0.23, 0.27, 0.29}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{arsenic}
\colorlet{accent}{arsenic}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
\newcommand{\cvproject}[1]{%
	{\textbf{\color{accent}#1}\par}
}
%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Duy Huynh}
\tagline{Machine Learning Engineer}
%\photo{2.5cm}{F1}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{\href{mailto:vndee.huynh@gmail.com}{vndee.huynh@gmail.com}}
  \linkedin{\href{https://linkedin.com/in/vndee}{vndee}}
  \github{\href{https://github.com/vndee}{vndee}} % I'm just making this up though.
  \phone{+84918451096}
  \location{Ho Chi Minh City, Vietnam}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

\cvsection[page1sidebar]{Experience}
\cvevent{\textbf{AI Engineer}}{Dai Phat Solutions Co., Ltd}{Nov 2018 -- Present}{Ho Chi Minh City, Vietnam}
\begin{itemize}
	\item Research, build and deploy AI solutions. 
	\item PyTorch, Flask, Django, FastAPI, Go Fiber, Jenkins, Git, Linux, Apache Kafka.
\end{itemize}
\smallskip
\smallskip
\cvevent{\textbf{Research Internship}}{AI Laboratory, Ton Duc Thang University}{Jun 2018 -- Nov 2018}{Ho Chi Minh City, Vietnam}
\begin{itemize}
	\item Doing research on topics about Natural Language Processing, as well as having hand-on experiences in CV, DGN and GNN. 
	\item PyTorch, Pandas, Numpy, Matplotlib.
\end{itemize}

\cvsection{Projects}
\cvproject{Sentivi - Tool for Sentiment Analysis} {Project Owner - \href{https://github.com/vndee/sentivi}{https://github.com/vndee/sentivi}}
\begin{itemize}
	\item A simple tool for sentiment analysis which is a wrapper of scikit-learn and PyTorch Transformers models. It is made for easy and faster pipeline to train and evaluate several classification algorithms. 
	\item PyTorch, Scikit-learn, Transformers, Numpy. 
\end{itemize}

\cvproject{Deepis - Deep Image Search} {Project Manager \& Developer}
\begin{itemize}
	\item End-to-end visual search service that empowers by state-of-the-art Deep Learning algorithm. It is designed for scale and stability. 
	\item PyTorch, Go Fiber, FastAPI, Apache Kafka,  Django, Selenium, Docker, Jenkins, HTML/CSS, Milvus, Elasticsearch, Kibana.
\end{itemize} 

\cvproject{Deepa - MOOCs platform} {Project Manager}
\begin{itemize}
	\item MOOCs (Massive Open Online Courses) platform that enhances high-level education based on OpenEdx open-source with containerizing deployment. 
	\item Docker, Django, HTML/CSS, Jenkins CI.
\end{itemize} 

\cvsection{Competitive Programming}
\cvproject{Codeforces Candidates Master} {}
\smallskip
\begin{itemize}
	\item Rating 2065 (top 4\%). \href{https://codeforces.com/profile/hdi}{https://codeforces.com/profile/hdi}.
\end{itemize}
\smallskip
\cvproject{Hackerrank Algorithm Specialist} {}
\begin{itemize}
	\item Top algorithm specialist of Hakerrank (rating 2268.76, rank 1678, top 1\%). \href{https://www.hackerrank.com/watagogo}{https://www.hackerrank.com/watagogo}.
\end{itemize} 


\clearpage



%% If the NEXT page doesn't start with a \cvsection but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the 
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}


\end{document}
